---
title: "demo2"
author: "Samuel Chan"
date: "7/18/2019"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggthemes)
```

## R Markdown
```{r}
loan <- read.csv("~/Desktop/loan.csv")
nrow(loan)
ncol(loan)
dim(loan)
```

```{r}
table(loan$credit_history)
```




```{r}
summary(loan)
```

```{r}
retail <- read.csv("workshop.csv")
head(retail)
```

```{r}
retail$Day.Index <- as.Date(retail$Day.Index)
retail$year <- as.factor(retail$year)
retail$DOW <- weekdays(retail$Day.Index)
retail$Month <- months(retail$Day.Index)
retail$isWeekend <- ifelse(retail$DOW == "Saturday" | retail$DOW == "Sunday", "Weekend", "Weekday")
str(retail)
```

```{r}
retail$DOW <- as.factor(retail$DOW)
retail$Month <- as.factor(retail$Month)
retail$isWeekend <- as.factor(retail$isWeekend)
head(retail)
```

```{r}
plot(x=retail$Day.Index, 
     y=retail$Sessions,
     type="l")
```


```{r}
plot(x=retail$Day.Index, 
     y=retail$Sessions,
     cex=0.7, pch=19)
```

```{r}
plot(x=retail$DOW, 
     y=retail$Sessions, col="hotpink4")
```



```{r}
ggplot(data=retail, aes(x=DOW, y=Sessions))+
  geom_boxplot() +
  geom_jitter(aes(col=DOW)) +
  labs(title="MiStore Traffic", 
       subtitle="Gathered from CRM, 2019", 
       caption="Created by Julia") +
  theme_economist_white()
```

Our Analyst Team has the following discovery:
- Sales is better in Q3  
- The new retail outlet consistent outperform other branches  
- Campaign was most successful in November 2018




```{r}
ggplot(data=retail, aes(x=DOW, y=Sessions))+
  geom_boxplot() +
  geom_jitter(aes(col=DOW)) +
  labs(title="MiStore Traffic", 
       subtitle="Gathered from CRM, 2019", 
       caption="Created by Julia") +
  coord_flip() +
  facet_wrap(~Month)
```

```{r}
head(mtcars)
```

```{r}
carmodel <- lm(formula=hp~mpg, 
             data=mtcars)
coef(carmodel)
```

```{r}
newcar <- data.frame(mpg=18)
print(newcar)
```

```{r}
predict(carmodel, newcar)
```


```{r}
plot(mtcars$mpg, mtcars$hp, pch=19)
abline(coef(carmodel)[1], coef(carmodel)[2], lty="dashed", col="blue")
```

```{r}
salary <- c(2500, 3500, 3000, 10000, 2000)
print(salary[-5])
```

```{r}
salary[c(1,3,4)]
```

```{r}
library(verisr2)
data(vcdb)
```

```{r}
dim(vcdb)
```

```{r}
getenum_stri(vcdb, "action.error.vector")[1:5]
```

```{r}
enum2grid(vcdb, c("asset.variety", "actor.external.variety"))
```

```{r}
tidy_vcdb <- collapse_vcdb(vcdb)
```

```{r}
id_small <- involving_country(vcdb, "ID", notes_only=TRUE)
id_small
```

- read.csv()
- str(), summary()
- dim()
- nrow(), ncol()
- plot(x=Month, y=Profit)
- plot(x, y, main="Profit Analysis", col="hotpink4", pch=1, cex=1)
- abline()
- external libraries such as ggplot
- installing and loading libraries
- comparison: R and Python
- machine learning
- lm(OilPrices ~ GasPrices, data=SGX)
- predict(model1, newdata)

















